XXXXX

### 2014-12-16 paper/RDF validation requirements/RDF validation requirements.tex
language tag operations
complexity

\section{Cardinality on Literal Language Tags}

@@

>>>>

\section{Language Tag Cardinality}

@@

\section{Exploiting Class/Property Specialization Ontology Axioms}

\begin{itemize}
	\item R-224-instance-level-data-validation-exploitingclass/property-specialization-axioms-in-ontologies
\end{itemize}

\begin{itemize}
  \item Validation of instances data (direct or indirect) exploiting the subclass or sub-property link in a given ontology.
  \item This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
\end{itemize}

\begin{itemize}
	\item If dc:date and one of its sub-properties dcterms:created or dcterms:issued are present, check that the value in dc:date is not redundant with dcterms:created or dcterms:issued for ingestion
  \item Check if dc:rights has the same value than edm:rights either as rdf:resource or literal, if yes dc:rights is redundant
  \item If one or more dc:coverage are present, suggest the use of one of its sub-properties, dcterms spatial or dcterms:temporal.
\end{itemize}
